---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# ozcran

<!-- badges: start -->
[![Travis build status](https://travis-ci.org/mdsumner/ozcran.svg?branch=master)](https://travis-ci.org/mdsumner/ozcran)
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/mdsumner/ozcran?branch=master&svg=true)](https://ci.appveyor.com/project/mdsumner/ozcran)
[![Codecov test coverage](https://codecov.io/gh/mdsumner/ozcran/branch/master/graph/badge.svg)](https://codecov.io/gh/mdsumner/ozcran?branch=master)
<!-- badges: end -->

The goal of ozcran is to check the status and packages available from Australian CRAN mirrors. 

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mdsumner/ozcran")
```
## Example

This is a basic example which gets the package list from Australian CRAN mirrors and
provides a quick summary. 

```{r example}
library(ozcran)

library(dplyr)
db <- oz_db() 

db %>% group_by(repos) %>% summarize(n = n(), date = max(as.Date(Published), na.rm = TRUE)) %>% arrange(desc(date))

```

---

  Please note that the 'ozcran' project is released with a
  [Contributor Code of Conduct](https://CODE_OF_CONDUCT.md).
  By contributing to this project, you agree to abide by its terms.
